Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-14 icse/paper.tex
Location and contents categories

\subsection{Code clone terminology}
In this study we use two concepts used to argue about code clones \cite{roy2007survey}:
\textbf{Clone instance}: A single cloned fragment.
\textbf{Clone class}: A set of similar clone instances.

@@

\subsubsection{Location}
The rationale for our categories regarding clone locations.

\subsubsection{Contents}
The rationale for our categories regarding clone contents.

>>>>

\subsection{Code clone terminology}
In this study we use two concepts used to argue about code clones \cite{roy2007survey}:
\\ \textbf{Clone instance}: A single cloned fragment.
\\ \textbf{Clone class}: A set of similar clone instances.

@@

\subsubsection{Location}
% The rationale for our categories regarding clone locations.

\begin{enumerate}
  \item \textbf{Method/Constructor Level:} A clone instance that does not exceed the boundaries of a single method or constructor.
  \item \textbf{Class Level:} A clone instance in a class, that exceeds the boundaries of a single method or contains something else in the class (like field declarations, other methods, etc.).
  \item \textbf{Interface/Enumeration Level:} A clone that is (a part of) an interface or enumeration.
\end{enumerate}

\subsubsection{Contents}
% The rationale for our categories regarding clone contents.

\begin{enumerate}
  \item \textbf{Full Method/Constructor/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
  \item \textbf{Partial Method/Constructor:} A clone that spans (a part of) the body of a method/constructor.
  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods.
  \item \textbf{Only Fields:} A clone that spans only global variables.
  \item \textbf{Other:} Anything that does not match with above-stated categories.
\end{enumerate}
